Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-21 GEMDataSource.Rmd
Trying to get stargazer to work well

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
library(xtable)
Table1 <- xtable(summary(CompleteDataset))
xtable(CompleteDataset, type = 'html')

library(stargazer)
stargazer(CompleteDataset, column.sep.width = "20pt", type = 'html')

>>>>

library(stargazer)
stargazer(CompleteDataset, column.separate = TRUE, type = 'html')
